% !TEX root = ../thesis-example.tex
%
\pdfbookmark[0]{Acknowledgement}{Acknowledgement}
\chapter*{Acknowledgement}
\label{sec:acknowledgement}
\vspace*{-10mm}
The unbelievable feeling of completing this work would never be possible without the help of so many amazing people I have met throughout my entire life. I hope with this few paragraphs I can express how immensely grateful I am for their guidance and support.

\qquad I would like to start by thanking my supervisors, Dr. Filipe B. Abdalla and Prof. Ofer Lahav, for their patience and for believing in my capacity to push forward such complex projects -- even in times when I did not believe it myself. It was one of my life goals to test the Standard Model of Cosmology by myself, they made that a reality together with great co-workers and collaborators like Bruno Moraes, Lorne Whiteway, Andreu Cuceu, Michael McLeod, Sreekumar Balan, Henrique Xavier, and Marc Manera.

\qquad No amount of words in this thesis could express how grateful I am for having Dr. Bruno Moraes as a mentor and as an acting second supervisor. Nothing in this thesis could have been achieved without Bruno's guidance, patience, close advice, discussions, and hard work (as I like to call those long discussions Bruno and I had, sometimes, to procrastinate together). Bruno helped me through complicated moments during my PhD, training me to be a good independent researcher and doing everything in his power, and sometimes even beyond it, to help me succeed. Valeu, Bruno!

\qquad A big eternal thanks to all my family, specially my mother, Maria Alice da Mota, and my grandparents, Irene e Porf\'irio da Mota, for believing in me, for understanding my urge to pursue my dreams, for the emotional support, and understanding you always provided me. The eternal `saudades' I feel for being away these almost three and a half years (and counting) can never be explained into words. For all the friends I left behind in that south of nowhere, I would like to thank you for never giving up on me, even during moments when I had given up myself. Thank you Vivian Pizzato, Gabriel Carpes (and all the Carpes family), Nicole de March, Rodrigo Sieben, Lucas Becker, Augusto Medeiros, Marcelo Fontoura, Andr\'e Gomes, Pedro Axelrud, Marcelo Pereira, Mauricio Goldstein, Sophie Collignon, Isadora Alves, Guilherme Kolinger, Debora Peretti, and so many more. Leaving you behind was the hardest thing I have ever done, I will never forget all the joy and support you all gave me through these years.

\qquad With an ocean away between where I used to consider home, I would like to thank a lot the amazing people that made me feel like UCL could be a new home. To the great friends I made from Group A, specially those who have a lot patience with me, I would like to thank: Felix Priestley, Luisa Lucie-Smith, Arianna Sorba, Niall Jeffrey, Will Jennings, Will Hartley, Tom Wilson, Michelle Lochner, Andreu Font-Ribera, Lorne Whiteway, Roger Wesson, Andrei Cuceu, Martin Rey, Harry Johnston, Constance Mahony, Krishna Naidoo, Holly Andrews, and many more. Other members of Group A, even though never at the pub with us, deserve more than a special thanks: Edd Edmondson and John Deacon for always helping me pronto to get my computer problems sorted; Kay Nakum for always helping me with every random enquire I have; and finally, Prof. Serena Viti and Dr. Andrew Pontzen for all the help and support. 

\qquad A special thanks to three very important people in this time and other periods of my life: my high school teacher, Mr. Jos\'e Ramiro Maciel, for making me so curious about science that I don't think I will ever give it up; my mentor, guru, and academic-father, Prof. Silvio R. Dahmen for all the guidance, advice, and pretty much teaching me how to be a better human being; and my long-term housemate Tarso Franarin for all the patience and friendship through these crazy London years.

\qquad Finally, a special thanks to Alberto de Campos e Silva at CNPq, all the people involved in the Science without Borders programme, and the Brazilian people who funded my PhD -- you made this dream a reality and I will never forget that.